## Basic Frequency Analysis

The analysis above was a bit dodgy since it dd not take into account the (slightly) different lengths of the documents.
Calculate the _proportions_ of each word 


```{r}
proportions_long <- 
  useful_words %>%
  count(year, word) %>%
  mutate(proportion = n / sum(n))  %>% 
  ungroup() %>% 
  select (-n)
```

Prepare data into word, year-x, year-y proprotion-x, proprotion-y
most suitable format for Tableau "facet - grid" style map

```{r}

proportions_cross <-
  inner_join(x = proportions_long, y = proportions_long, by = "word") %>% 
  select(word, year.x, year.y, proportion.x, proportion.y) %>% 
  filter (year.x != year.y) %>% 
  left_join(hot_words, by = "word")

#write_csv(proportions_cross, path = "CSVs/proportions_cross.csv")
proportions_cross
```


```{r}
proportions <- 
 proportions_long %>%
  spread(year, proportion) %>%
  left_join(hot_words, by = "word") %>% 
  mutate(category = ifelse(is.na(category), 'none', category))

proportions
```


```{r}

# the proportion_comparison16 dataset  makes it possible to compare  the 2016 proportions 
# against the  earlier years. 
proportion_comparison16  <-
  proportions %>% gather(year, proportion, `2010`:`2015`)

proportion_comparison16
```

Plot 2016 frequencies against the previous years.

```{r}
ggplot(proportion_comparison16, aes(x = proportion, y = `2016`, color = abs(`2016` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent) +
  scale_y_log10(labels = percent) +
  scale_color_gradient(limits = c(0,0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~year, ncol = 3) +
  labs(y = "2016", x = NULL) +
  theme_light() +
  theme(legend.position = "none") +
  ggtitle(label =   "Word popularity in 2016 report against previous years",
           subtitle = "Words above and to the left of the dotted line are more common in 2016 than previous years.")

```

Focus on the hot words.  Show these  in different colour based on category and  label these only.

```{r}
comp16_short <-  proportion_comparison16 %>% filter(year %in% c("2010", "2012", "2014"))
comp16_short_cold <-  comp16_short %>%  filter(category == "none")
comp16_short_hot <-  comp16_short %>%  filter(category != "none")

p <- brewer.pal(4, "Dark2") 
legend_colours <- c(climate = p[1], conduct = p[2], diversity = p[3], risk = p[4], none = "grey80")
legend_order <- c("climate", "conduct", "diversity", "risk", "none")
ggplot(comp16_short, aes(x = proportion, y = `2016`, color = category)) +
  geom_abline(color = "gray40", lty = 2) + 
  # show the cold words as a mainly transparent jittered background
  geom_jitter(data = comp16_short_cold, alpha = 0.3, size = 2.5, width = 0.3, height = 0.3) +
  # show the hot words exactly on location (no jitter) in the category colour
  geom_text(data = comp16_short_hot, aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  # show the hot word labels
  geom_point(data = comp16_short_hot, alpha = 0.8) +
  scale_x_log10(labels = percent) +
  scale_y_log10(labels = percent) +
  scale_color_manual(values = legend_colours, breaks = legend_order)  +
  #scale_color_gradient(limits = c(0,0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~year, ncol = 3) +
  labs(y = "2016", x = NULL) +
  theme_light() +
  theme(legend.position = "bottom") +
  ggtitle(label =   "Frequency of hot words in 2016 vs previous year's reports",
          subtitle = "Note that the choice of hot words is subjective and reflects the analyst's view.")

```
