## CRR 40 Acronyms

## Bank Buzzword Bingo 

Our test for acronyms is those words that have two or more consecutive letters in capitals.

```{r}
case_sense_words <-
  parsed_pages  %>% 
  unnest_tokens(word, page, to_lower = FALSE) %>% 
  mutate(word = str_extract(word, "[A-Za-z']+")) %>%  
  filter(!is.na(word)) %>% 
  anti_join(all_stop_words, by = "word")


acronyms <- case_sense_words %>% 
  filter(str_detect(word, "[A-Z][A-Z]")) %>% 
  count(word, sort = TRUE) %>% 
  mutate(ranking = min_rank(desc(n))) %>%
  ungroup() 

```

Let's make a word cloud  of these.
```{r}
acronyms %>%
  filter(!word %in% c("USD", "CHF", "AG")) %>% 
  with(wordcloud(word, n, max.words = 400))
```

Plot the top top acronyms in each year.

```{r fig.width = 10, fig.height = 12}
case_sense_words %>% 
  filter(str_detect(word, "[A-Z][A-Z]")) %>% 
  count(year, word, sort = TRUE) %>%  # counting by year and word this time
  # ungroup() %>% 
  group_by(year) %>% 
  arrange(desc(n)) %>%
  top_n(20, n)  %>% 
  ungroup()  %>% 
  mutate(word_year = fct_reorder(paste(word, year, sep = "__"), n)) %>% 
  ggplot(aes(x = word_year, 
             y = n, 
             fill = year)) + 
  geom_col() +
  facet_wrap(~year, ncol = 4, scales = "free") +
  ggtitle("Most Popular Acronyms Over The Years", 
          "How many do you know?") +
  scale_y_continuous("Number") +
  scale_x_discrete("Year of report", 
                   labels = function(x) str_replace(x, "__.*", "")) +
  #scale_fill_tableau(palette = "tableau10medium") +
  scale_fill_manual(values = brewer.pal(7, "Dark2")) +
  coord_flip() +
  theme_light() +
  theme(legend.position = "bottom")  +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

```

### Forensic Analysis
Let's find some of the defnitions of these acronyms

There seems to be a house style in that the first time an acronym appears, it is in brackets with the definition preceding it
e.g. the New York Stock Exchange (NYSE) 

```{r out.width=300}

# this pattern captures acronyms and the preceding 5 words
p_acronym_and_definition <- 
  capture(one_or_more(WRD)) %R% 
  SPACE %R%
  capture(one_or_more(WRD)) %R% 
  SPACE %R%
  capture(one_or_more(WRD)) %R% 
  SPACE %R%
  capture(one_or_more(WRD)) %R% 
  SPACE %R%
  capture(one_or_more(WRD)) %R% 
  SPACE %R%  
  OPEN_PAREN %R% capture(one_or_more(UPPER)) %R% CLOSE_PAREN

# the list_result column with have a contain a matrix of n rows by 5 columns
# n depends on the mumber of matches
# unnest will not accept a list of matrices but will accepts a list of data frames
# so to unnest so that each match is on own row, we must convert the matrix into a data_frame

convert_to_df7 <- function (m) {
  data_frame(text = m[,1], 
             word1 = m[,2],
             word2 = m[,3],
             word3 = m[,4],
             word4 = m[,5],
             word5 = m[,6],
             acronym = m[,7])
}


# boring_terms <- "[The |the |of |on |in |and |for ]"
boring_terms <- or("The ","the ","of ","on ","in ","and ","for ", "a ")
empty_term <-  ""

parsed_pages_unbored <- 
  parsed_pages %>% 
 mutate(page2 = str_replace_all(page, boring_terms, empty_term))

parsed_pages_with_nests <-
  parsed_pages_unbored %>% 
  mutate(list_result = str_match_all(page2, p_acronym_and_definition)) %>% 
  mutate(tibble_result = map(list_result, convert_to_df7))

# select(parsed_pages, pagenumber, list_result, tibble_result)

acronym_definitions <- 
  parsed_pages_with_nests %>% 
  unnest(tibble_result)

acronym_definitions %>% 
  select(year, pagenumber, acronym, word1, word2, word3, word4, word5) %>% 
  knitr::kable()
```
